---
title: "Exercise-1"
author: "Anonymous - MY472"
date: "2024-10-27"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Data 

For this transformation we will use a built-in R dataset, namely "sleep" reporting on the effect of two soporific drugs on a sample of 10 students. 

```{r loading data, message = F}
library(tidyverse)
data("sleep")
```

## Transforming Data

We will now create a function to transform this data. We want the function to filter through the data to only show the effect on group 2.

```{r function}
only_group2 <- function(data){
  data <- data %>% 
    filter(group == 2)
  return (data)
}

only_group2(sleep)
```
The effect of the drug on the 2nd group results in an average increase of `r mean(only_group2(sleep)$extra)` hours of sleep.

## New function

We now want create a second function to separate the effect on group 1 this time.

```{r another function}
only_group1 <- function(data_new){
  data_new <- data_new %>% 
    filter(group == 1)
  return (data_new)
}

only_group1(sleep)
```

The effect of the drug on the 1st group results in an average increase of `r mean(only_group1(sleep)$extra)` hours of sleep.
